Rhyme: A Query Language for Nested Data Structures

### 2024-12-16 paper.tex
Minor update

Section \ref{evaluation} evaluates the generated code by comparing it with TACO and highlights the differences.\par

@@

\item \textbf{Tensor type}: To support both sparse and dense tensor algebra, \rhyme introduces tensor types, denoted as $T = \langle \emph{mode}, \emph{dims}, \emph{elemTy} \rangle$. A tensor type is a tuple consisting of: \begin{itemize} \item \emph{mode}: Indicates whether the tensor is sparse or dense. \item \emph{dims}: Represents the dimensions of the tensor; \rhyme supports tensors with arbitrary dimensions. \item \emph{elemTy}: Specifies the element type of the tensor, which can be any numeric type. \end{itemize}

@@

The \rhyme compiler selects an efficient co-iteration strategy for different generators based on the dense/sparse patterns of the data sources. Combined with \rhyme's backend loop scheduling and fusion optimizations, this approach enables the specialized generation of high-performance code for sparse tensor algebra within a multi-paradigm language framework.

>>>>

Section \ref{evaluation} evaluates the generated code of sparse tensor algebra by comparing it with TACO.\par

@@

\item \textbf{Tensor type}: To support both sparse and dense tensor algebra, \rhyme introduces tensor types, denoted as $T = \langle \emph{mode}, \emph{dims}, \emph{elemTy} \rangle$. A tensor type is a tuple consisting of: \begin{itemize} \item \emph{mode}: Indicates whether the tensor is sparse or dense. \item \emph{dims}: Represents the dimensions of the tensor; \rhyme supports tensors with arbitrary dimensions. \item \emph{elemTy}: Specifies the element type of the tensor, which can be any number type. \end{itemize}

@@

The \rhyme compiler selects an efficient co-iteration strategy for different generators based on the sparsity patterns of the data sources. Combined with \rhyme's backend loop scheduling and fusion optimizations, this approach enables the specialized generation of high-performance code for sparse tensor algebra within a multi-paradigm language framework.
